---
title: "Download_Process_rRNA_labeled"
author: "Michael Mann"
date: "9/20/2021"
output: html_document
---
Some of the genomes already include the rRNA genes. So I will download those files, process them and then 
```{r setup}
library(tidyverse)
library(microseq)
```

Running this on CARC at 
/users/mimann/wheeler-scratch/genomes/raw_genomes
to download the genomes.
rRNA_download_script.pbs
```{bash download asco rrna seqs}
#!/bin/bash

#PBS -q default
#PBS -l nodes=1:ppn=8
#PBS -l walltime=1:00:00
#PBS -N x_rRNA_downloads
#PBS -m ae
#PBS -M mimann@unm.edu

module load parallel-20170322-gcc-4.8.5-2ycpx7e

source $(which env_parallel.bash)

src=$PBS_O_WORKDIR
# exports to fna_files folder
cat $src/asco_genomes.txt $src/asco_rna_from_genomes.txt $src/basidio_rrna_genomes.txt| env_parallel --sshloginfile $PBS_NODEFILE 'wget {} -P $src/fna_files --no-verbose'


```

I did unzip it at first but there is no need to.

Wrote an R script to run in parallel on CARC. Cleaned up and only kept rRNA sequences. 
Creates tibble and stores it in the rna_annotations_genomes.rds object.
```{bash clean up r}
#!/bin/bash

#PBS -q default
#PBS -l nodes=1:ppn=8
#PBS -l walltime=4:00:00
#PBS -N x_filter_using_R
#PBS -m ae
#PBS -M mimann@unm.edu


module load r-4.0.4-gcc-10.2.0-python3-dghog6f

cd $PBS_O_WORKDIR

# simple script to pull out the relevant rRNA genes. 
# this is all done on CARC because my computer has no storage and CARC can run in parallel!
Rscript Filter_rna_genome_files.R

```


```{r read in rds}
# NAs mean the genome lacked any rRNA seqs
rRNA_annotations <- read_rds("Downloading_rRNA/rna_annotations_genomes.rds")

```

