---
title: "Checking_test_set"
author: "Michael Mann"
date: '2022-06-21'
output: html_document
---
Checking test set and phylogenomic with EPA-ng placement provided by T-BAS using the AFTOL tree. 
Looking for taxa that aligned poorly or seem to be errors. 
Runtime options

info form the job:
runnumber is: JBDTSRBW
annotation is: EPA_using_fungal_reference_18S
ladderize_option: ladderize
unknown_fasta1 is test_set_18S_TBAS.fasta.
Placement cutoff distance is skip.
Placement program wall time is 168.0.
BLAST filter run is none.
Substitution model: GTRGAMMA.
Generic parameter: noneselected.
Phylogeny program: epang.
Cluster on one locus (used only on multilocus): cluster_all.
Data type is: DNA.
Cluster program is: vsearch.
similarity cutoff is auto.
Add to OTUS is not checked.
Placement option is likelihood.
Outgroup is Monosiga_brevicollis, Caenorhabditis_elegans, Drosophila_melanogaster, Ciona_intestinalis, Homo_sapiens, Dictyostelium_discoideum, Cryptosporidium_parvum, Toxoplasma_gondii, Phytophthora_sojae, Thalassiosira_pseudonana, Cyanidioschyzon_merolae, Chlamydomonas_reinhardtii, Oryza_sativa, Arabidopsis_thaliana, Populus_trichocarpa
Reference set is: Fungi
Reference partitions is nucSSU


```{r setup, include=FALSE}
library(tidyverse)

```


```{r read in data}
epa_placement_SSU <- read_csv("Test_Set/epa_ng/T-BAS_Online_check/SSU/tbas21_archiveJBDTSRBW_/assignments_reportJBDTSRBW.csv")
epa_placement_LSU <- read_csv("Test_Set/epa_ng/T-BAS_Online_check/LSU/tbas21_archiveGUNJYJCA_/assignments_reportGUNJYJCA.csv")
test_set_taxonomy <- read_csv("/Users/michaelmann/Dropbox/Masters_Program/Genomes_rRNA/Test_Set/Test_Dataset_taxonomy.csv")

```

Using epa-ng on TBAS to place taxa onto 
```{r merge and view}


epa_placement_LSU %>%
  mutate(`Query sequence` = str_remove(`Query sequence`, "Phylogenomic_")) %>%
  full_join(test_set_taxonomy, by = c(`Query sequence` = "phylo_tip")) %>%
  mutate(Order_match =  `Order-level assignment` == order) %>%
  write_csv("Test_Set/epa_ng/T-BAS_Online_check/LSU/merged_LSU_EPA-NG_test_set_taxonomy_mismatched_order.csv")


epa_placement_SSU %>%
  mutate(`Query sequence` = str_remove(`Query sequence`, "Phylogenomic_")) %>%
  full_join(test_set_taxonomy, by = c(`Query sequence` = "phylo_tip")) %>%
  mutate(Order_match =  `Order-level assignment` == order) %>%
  write_csv("Test_Set/epa_ng/T-BAS_Online_check/SSU/merged_SSU_EPA-NG_test_set_taxonomy_mismatched_order.csv")

```
